Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-05 paper_comparison/paper_comparison/paper_comparison.tex
polish the residual departure

There are many departures from a good residual plot, but we will
consider only three types of them in this paper, which are also the most
commonly checked departures for a residual plot. The first one is
non-linearity. Any unnatural non-linear curve presented in the residual
plot could be considered an indicative of non-linearity. At the
top-right of Figure {[}ref here{]}, there is an example residual plot of
this type of departure. The second type of departure we will consider is
heterskedasticity. The usual pattern of this type of departure is the
inconsistent distribution of the residuals for different x values.
Visually, it usually results in the so-called ``butterfly'' shape as
shown in the bottom-left panel of Figure {[}ref here{]}, or the
``triangle'' shape where the smallest variance occurs at the edges of
the x-axis. The last type of departure is non-normality. This departure
is usually harder to be detected from the residuals plot compared to
non-linearity and heterskedasticity. In most the case, a
quantile-quantile plot can do a better job. Depending on the actual
distribution of the residuals, different visual patterns will be
discovered. If the distribution is skewed, one will see some outliers
presented on only one side of the zero line as shown in the bottom-right
of Figure {[}ref here{]}.

>>>>

There are many types of departures from a good residual plot. Three of
them will be considered in this paper, which are also the most commonly
checked departures for a residual plot. The first one is non-linearity.
Any unnatural and non-linear functional form of residuals on fitted
values presented in the residual plot could be considered as an
indicative of non-linearity. At the top-right of Figure {[}ref here{]},
there is an example residual plot of this type of departure. The second
type of departure that will be considered is heterskedasticity. The
usual pattern is the inconsistent distribution of the residuals for
different x values. Visually, it sometimes results in the so-called
``butterfly'' shape as shown in the bottom-left panel of Figure {[}ref
here{]}, or the ``triangle'' shape where the smallest variance occurs at
the edges of the x-axis. The last type of departure we will consider is
non-normality. This departure is usually harder to be detected from the
residuals plot compared to non-linearity and heterskedasticity. In most
cases, a quantile-quantile plot can do a better job. Depending on the
actual distribution of the residuals, different visual patterns will be
discovered. Readers of the residuals plot will notice the data points do
not distribute noramlly on the y-axis. For example, if the distribution
is skewed, one will see the ``tail'' of the distribution as some
outliers presented on only one side of the zero line as shown in the
bottom-right of Figure {[}ref here{]}.
